Estimating Output Loss due to being Unrecognized as States

### 2019-03-07 paper/paper.tex
Describe the history of Karabakh #51

\section{Data}
\subsection{Real GDP}
We use the Penn World Table 9.0 (Freenstra et al.\ 2015), as the data source for real GDP. 
Expenditure-side real GDP at chained PPPs in 2011 US dollars (the variable \textit{rgdpe}) is used because the variable is meant for comparing ``living standards across countries and across years'' (Freenstra et al.\ 2015, Table 1).

@@

\begin{thebibliography}{99}                                                                                                %
\bibitem{} Alesina, Alberto, Stelios Michalopoulos, and Elias Papaioannou. 2016. ``Ethnic Inequality.'' \textit{Journal of Political Economy}, 124(2): 428-488.
\bibitem{} Bickenbach, Frank, Eckhardt Bode, Peter Nunnenkamp, and Mareike Soder. 2016. ``Night lights and regional GDP.'' \textit{Review of World Economics}, 152 (2), 425-447.                                                                                         
\bibitem{} Cameron, A. Colin, Jonah B. Gelbach, and Douglas L. Miller. 2011. ``Robust Inference With Multiway Clustering.'' \textit{Journal of Business \& Economic Statistics}, 29(2): 238-249.
\bibitem{} Dreher, Axel, Andreas Fuchs, Roland Hodler, Bradley C. Parks, Paul A. Raschky, and Michael J. Tierney. 2015. ``Aid on Demand: African Leaders and the Geography of China?s Foreign Assistance.'' CEPR Discussion Paper, 10170.
\bibitem{} Feenstra, Robert C., Robert Inklaar, and Marcel P. Timmer. 2015. ``The Next Generation of the Penn World Table.'' \textit{American Economic Review}, 105(10): 3150-3182.
\bibitem{} GADM. 2018. ``GADM Maps and Data (version 3.6).'' https://gadm.org (accessed February 7, 2019).
\bibitem{} Goldblatt, Ran, Kilian Heilmann, and Yonatan Vaizman. 2018. ``Can Medium-Resolution Satellite Imagery Measure Economic Activity at Small Geographies? Evidence from Landsat in Vietnam.'' \textit{World Bank Economic Review}, forthcoming.
\bibitem{} Henderson, J. Vernon, Adam Storeygard, and David N. Weil. 2012. ``Measuring Economic Growth from Outer Space.'' \textit{American Economic Review}, 102(2): 994-1028.
\bibitem{} Hodler, Roland, and Paul A. Raschky. 2014. ``Regional Favoritism.'' \textit{Quarterly Journal of Economics}, 129(2): 995-1033.
\bibitem{} Mellander, Charlotta, Jose Lobo, Kevin Stolarick, and Zara Matheson. 2015. ``Night-Time Light Data: A Good Proxy Measure for Economic Activity?'' \textit{PloS one}, 10(10), e0139779.
\bibitem{} National Geophysical Data Center. 2015. ``Version 4 DMSP-OLS Nighttime Lights Time Series.'' National Oceanic and Atmospheric Administration. https://ngdc.noaa.gov/eog/dmsp/downloadV4composites.html (accessed February 6, 2019).
\bibitem{} Pinkovskiy, Maxim, and Xavier Sala-i-Martin. 2016. ``Newer Need Not be Better: Evaluating the Penn World Tables and the World Development Indicators Using Nighttime Lights.''. NBER Working Paper, 22216.
\bibitem{} Storeygard, Adam. 2016. ``Farther on down the Road: Transport Costs, Trade and Urban Growth in Sub-Saharan Africa.'' \textit{The Review of Economic Studies}, 83(3): 1263-1295.
\bibitem{} Witmer, Frank D.W., and John O?Loughlin. 2011. ``Detecting the Effects of Wars in the Caucasus Regions of Russia and Georgia Using Radiometrically Normalized DMSP-OLS Nighttime Lights Imagery.'' \textit{GIScience \& Remote Sensing}, 48(4): 478-500.
\bibitem{} World Bank. 2018. \textit{World Development Indicators}. http://wdi.worldbank.org (accessed February 27, 2019).
\end{thebibliography}

>>>>

\section{Background}
\subsection{Nagorno-Karabakh}
Nagorno-Karabakh is a mountainous enclave of Armenian people in the west of Azerbaijan. Armenians are culturally different from Azerbaijanis in terms of religion (Armenian Orthodox Christianity versus Islam, mostly Shia) and language (Armenian vs Turkish).

In 1923, the Soviet Union's authority drew the border of Nagorno-Karabakh Autonomous Oblast from scratch, based on their understanding of where Armenians resided within Azerbaijan.%
\footnote{
	An autonomous oblast is a district with some degree of autonomy from the government of a constituent republic of the Soviet Union. 
} 
The Soviet leaders made Nagorno-Karabakh part of Azerbaijan, rather than of Armenia, for two reasons, according to de Waal (2013: 144-145). First, Moscow needed to appease Azeri politicians to control their oil fields in the Caspian Sea. Second, Armenians in Nagorno-Karabakh economically relied on the eastern part of Azerbaijan, and the communist ideal dictated that economic consideration should override ethnic integration.

During the Soviet days, the Azerbaijani authority encouraged the migration of Azeris into Nagorno-Karabakh. Population of Azerbaijanis in Nagorno-Karabakh jumped up from 13,000 in 1926 to 37,000 in 1979 while the corresponding figures for Armenians are 117,000 and 123,000, respectively (de Waal 2013: 153-154). The Azeri authority also ignored the Armenian culture in Nagorno-Karabakh: there was no Armenian-language television channel; the history of Armenia not taught in Armenian-language schools; medieval Armenian churches closed and crumbling (de Waal 2013: 154).

The breakup of the Soviet Union consequently unleashed the complaints of Karabakh Armenians against these Azerbaijani government policies. The local government of Nagorno-Karabakh declared independence two days after Azerbaijan declared its independence from the Soviet Union on August 30, 1991. The vast majority of people in Nagorno-Karabakh voted yes in a referendum on independence on December 10. The Azeri government did not accept the secessionist move by Karabakh Armenians, resulting in the war of secession from 1992 to 1994.

The 1994 ceasefire line was drawn based on the territory that Karabakh's army occupied by the end of the war. It significantly differs from the Soviet-era boundary of Nagorno-Karabakh as Karabakh Armenians have occupied the large chunk of land in the south-west corner of Azerbaijan to be geographically contiguous with Armenia.

One consequence of the War of Secession is ethnic homogenization on both sides of the border. It is estimated that approximately 500,000 Azerbaijanis were displaced from the occupied part of Azerbaijan while 353,000 Armenians were displaced from the rest of Azerbaijan.%
\footnote{
	These numbers are based on Arif Yunusov's calculations, cited by de Waal (2013: 327).
}
\section{Data}
\subsection{Real GDP}
We use the Penn World Table 9.0 (Freenstra et al.\ 2015), as the data source for real GDP. 
Expenditure-side real GDP at chained PPPs in 2011 US dollars (the variable \textit{rgdpe}) is used because the variable is meant for comparing ``living standards across countries and across years'' (Freenstra et al.\ 2015, Table 1).

@@

\begin{thebibliography}{99}                                                                                                %
\bibitem{} Alesina, Alberto, Stelios Michalopoulos, and Elias Papaioannou. 2016. ``Ethnic Inequality.'' \textit{Journal of Political Economy}, 124(2): 428-488.
\bibitem{} Bickenbach, Frank, Eckhardt Bode, Peter Nunnenkamp, and Mareike Soder. 2016. ``Night lights and regional GDP.'' \textit{Review of World Economics}, 152 (2), 425-447.                                                                                         
\bibitem{} Cameron, A. Colin, Jonah B. Gelbach, and Douglas L. Miller. 2011. ``Robust Inference With Multiway Clustering.'' \textit{Journal of Business \& Economic Statistics}, 29(2): 238-249.
\bibitem{} de Waal, Thomas. 2013. \textit{Black Garden: Armenia and Azerbaijan through Peace and War} (Revised Edition). New York: New York University Press.
\bibitem{} Dreher, Axel, Andreas Fuchs, Roland Hodler, Bradley C. Parks, Paul A. Raschky, and Michael J. Tierney. 2015. ``Aid on Demand: African Leaders and the Geography of China?s Foreign Assistance.'' CEPR Discussion Paper, 10170.
\bibitem{} Feenstra, Robert C., Robert Inklaar, and Marcel P. Timmer. 2015. ``The Next Generation of the Penn World Table.'' \textit{American Economic Review}, 105(10): 3150-3182.
\bibitem{} GADM. 2018. ``GADM Maps and Data (version 3.6).'' https://gadm.org (accessed February 7, 2019).
\bibitem{} Goldblatt, Ran, Kilian Heilmann, and Yonatan Vaizman. 2018. ``Can Medium-Resolution Satellite Imagery Measure Economic Activity at Small Geographies? Evidence from Landsat in Vietnam.'' \textit{World Bank Economic Review}, forthcoming.
\bibitem{} Henderson, J. Vernon, Adam Storeygard, and David N. Weil. 2012. ``Measuring Economic Growth from Outer Space.'' \textit{American Economic Review}, 102(2): 994-1028.
\bibitem{} Hodler, Roland, and Paul A. Raschky. 2014. ``Regional Favoritism.'' \textit{Quarterly Journal of Economics}, 129(2): 995-1033.
\bibitem{} Mellander, Charlotta, Jose Lobo, Kevin Stolarick, and Zara Matheson. 2015. ``Night-Time Light Data: A Good Proxy Measure for Economic Activity?'' \textit{PloS one}, 10(10), e0139779.
\bibitem{} National Geophysical Data Center. 2015. ``Version 4 DMSP-OLS Nighttime Lights Time Series.'' National Oceanic and Atmospheric Administration. https://ngdc.noaa.gov/eog/dmsp/downloadV4composites.html (accessed February 6, 2019).
\bibitem{} Pinkovskiy, Maxim, and Xavier Sala-i-Martin. 2016. ``Newer Need Not be Better: Evaluating the Penn World Tables and the World Development Indicators Using Nighttime Lights.''. NBER Working Paper, 22216.
\bibitem{} Storeygard, Adam. 2016. ``Farther on down the Road: Transport Costs, Trade and Urban Growth in Sub-Saharan Africa.'' \textit{The Review of Economic Studies}, 83(3): 1263-1295.
\bibitem{} Witmer, Frank D.W., and John O?Loughlin. 2011. ``Detecting the Effects of Wars in the Caucasus Regions of Russia and Georgia Using Radiometrically Normalized DMSP-OLS Nighttime Lights Imagery.'' \textit{GIScience \& Remote Sensing}, 48(4): 478-500.
\bibitem{} World Bank. 2018. \textit{World Development Indicators}. http://wdi.worldbank.org (accessed February 27, 2019).
\end{thebibliography}
